Off-target spray particle movement

### 2021-08-04 manuscript.tex
as

\title{Off-target spray particle movement}
\author{Rodrigo Werle \and Bruno C Vieira \and Maxwel C.
Oliveira \and Guilherme Alves \and Greg Kruger}
\date{2021-07-15}

@@

Integrate pest management The off-target particle movement

The objective of this stu

@@

The statistical analyses were conducted with R statistical software
version 4.1.0.\textsuperscript{1} Data analyses were performed with
Bayesian inference with ``brms'' package.\textsuperscript{2} Bayesian
inference uses Markov chain Monte Carlo algorithms for sampling a
probability distribution;\textsuperscript{2} and avoids singular fit
from frequentist linear models when using complex random effects.

@@

Data was fitted to a mixed model using \emph{brm} function. Treatments
were the fixed effects and blocks nested within location random effects.
Model family was gaussian and prior distribution was set to student-t
with mean 0.5, standard deviation 3 and 11 degrees of freedom. The
posterior summaries (mean and highest posterior density) were estimated
with \emph{emmeans} function from the ``emmeans'' package. Treatment
means were compared using Bayes Factor (BF).\textsuperscript{3,4} In
short, if BF \textgreater{} 1 there is evidence for H1 (difference
between treatments); whereas, if H0 \textless{} 1 there is evidence for
H0 (no difference between treatments). If BF = 1, there is no evidence.
The level of evidence (anecdotal, moderate, strong, very strong, and
extreme) varies as the BF value increases (evidence for H1) or decreases
(evidence for H0).

@@

The area under the curve (AUC) was used to validate the linear models.
The spray solution deposition across distances within an experimental
unit were used to calculate the absolute AUC value. The AUC was
performed with \emph{audps} function from the ``agricolae'' package. The
AUC is commonly used for plant disease progress\textsuperscript{5,6} but
has been used to calculate herbicide injury.\textsuperscript{7} Data was
fitted to a mixed model using \emph{brm} function. Treatments were the
fixed effects and blocks nested within location random effects. Model
family was gaussian and prior distribution was set to student-t with
mean 0.5, standard deviation 3 and 11 degrees of freedom. The posterior
summaries and treatment means were estimated and compared using Bayes
Factor (BF) as above-mentioned.

@@

The Dv(10,50,90), RS, and \% drifable fines was fitted to a Bayesian
linear mixed model using \emph{brm} function. In the models, solution
and nozzle were set as fixed effects. Model family was hurdle gamma and
prior distribution was set to student-t with mean 0.5, standard
deviation 1 and 2 degrees of freedom. For each response variable, two
models were fitted: with and without interaction (solution and nozzle).
A model comparison was made with \textbf{bayesfactor\_models} from
``bayestestR'' package\textsuperscript{8} to investigate interaction
significance. For all response variables (Dvs, RS and \% drifable
fines), the best model was with interaction. The posterior summaries and
treatment means were estimated and compared using Bayes Factor (BF) as
above-mentioned.

@@

\hypertarget{spray-solution-deposition-at-inswath-and-upwind-1}{%
\subsection{Spray solution deposition at inswath and
upwind}\label{spray-solution-deposition-at-inswath-and-upwind-1}}

@@

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-LanguageEnvironmentStatistical2021}{}%
\CSLLeftMargin{1 }
\CSLRightInline{R: {A Language} and {Environment} for {Statistical
Computing}, {R Foundation for Statistical Computing}, {Vienna, Austria}
(2021).}

\leavevmode\hypertarget{ref-burknerBrmsPackageBayesian2017}{}%
\CSLLeftMargin{2 }
\CSLRightInline{Bürkner P-C, \textbf{Brms} : {An} {\emph{R}} {Package}
for {Bayesian Multilevel Models Using} {\emph{Stan}}, \emph{J Stat Soft}
\textbf{80} (2017).}

\leavevmode\hypertarget{ref-leeBayesianCognitiveModeling2014}{}%
\CSLLeftMargin{3 }
\CSLRightInline{Lee MD and Wagenmakers E-J, Bayesian {Cognitive
Modeling}: {A Practical Course}, {Cambridge University Press} (2014).}

\leavevmode\hypertarget{ref-kassBayesFactors1995}{}%
\CSLLeftMargin{4 }
\CSLRightInline{Kass RE and Raftery AE, Bayes {Factors}, \emph{Journal
of the American Statistical Association} \textbf{90}:773--795,
{{[}American Statistical Association, Taylor \& Francis, Ltd.{]}}
(1995).}

\leavevmode\hypertarget{ref-meenaAreaDiseaseProgress2011}{}%
\CSLLeftMargin{5 }
\CSLRightInline{Meena PD, Chattopadhyay C, Meena SS, and Kumar A, Area
under disease progress curve and apparent infection rate of {Alternaria}
blight disease of {Indian} mustard ({Brassica} juncea) at different
plant age, \emph{Archives of Phytopathology and Plant Protection}
\textbf{44}:684--693, {Taylor \& Francis} (2011).}

\leavevmode\hypertarget{ref-simkoAreaDiseaseProgress2011}{}%
\CSLLeftMargin{6 }
\CSLRightInline{Simko I and Piepho H-P, The {Area Under} the {Disease
Progress Stairs}: {Calculation}, {Advantage}, and {Application},
\emph{Phytopathology®} \textbf{102}:381--389, {Scientific Societies}
(2011).}

\leavevmode\hypertarget{ref-striegelSpraySolutionPH2021}{}%
\CSLLeftMargin{7 }
\CSLRightInline{Striegel S, Oliveira MC, Arneson N, Conley SP,
Stoltenberg DE, and Werle R, Spray solution {pH} and soybean injury as
influenced by synthetic auxin formulation and spray additives,
\emph{Weed Technol} \textbf{35}:113--127 (2021).}

\leavevmode\hypertarget{ref-makowski2019}{}%
\CSLLeftMargin{8 }
\CSLRightInline{Makowski D, Ben-Shachar M, and Lüdecke D, {bayestestR}:
{Describing Effects} and their {Uncertainty}, {Existence} and
{Significance} within the {Bayesian Framework}, \emph{JOSS}
\textbf{4}:1541 (2019).}

>>>>

\title{Off-target spray particle movement}
\author{Rodrigo Werle \and Bruno C Vieira \and Maxwel C.
Oliveira \and Guilherme Alves \and Greg Kruger}
\date{2021-08-04}

@@

The widespread cases of glyphosate-resistant weeds throughout the US
motivated farmers to adopt dicamba and 2,4-D tolerant
crops.\textsuperscript{1--5} As expected, the agricultural usage of
dicamba and 2,4-D significantly increased in the US (``United States
Department of Agriculture'' 2020). Applications of dicamba and 2,4-D in
new cropping areas during extended time in the growing season has led to
increased opportunities for the off-target movement of these
herbicides.\textsuperscript{6,7} Spray drift is one of the main
mechanisms of pesticide off-target movement and can be defined as the
part of the pesticide application deflected away from the target area
during or following applications.\textsuperscript{8} Herbicide drift
potential is influenced by application technique, environmental
conditions, and surrounding vegetation.\textsuperscript{9--13}

Dicamba and 2,4-D spray drift is a concern because these herbicides are
very active on broadleaf vegetation, including soybean and cotton,
causing distinctive crop injury and yield loss at very low dose
exposures.\textsuperscript{14} The adoption of best management practices
during herbicide applications, including proper nozzle selection and the
use of drift reducing adjuvants, are among the main strategies to manage
spray droplet size and mitigate spray drift.\textsuperscript{15--17} New
dicamba and 2,4-D products are mostly applied using venturi nozzles with
air-inclusion and pre-orifice components that increase spray droplet
size and reduce spray drift potential.\textsuperscript{18,19} Despite
the advances in nozzle technology,\textsuperscript{19} pesticide
formulations and adjuvants,\textsuperscript{17} spraying
techniques,\textsuperscript{20} strategies to mitigate spray
drift,\textsuperscript{11} and education and extension
efforts,\textsuperscript{4,21} dicamba and 2,4-D spray drift remains
associated with crop injury complaints across the US. In addition to
this, common practices to mitigate spray drift, such as the use of DRAs
with venturi nozzles in combination with lower pressures and boom
heights, could potentially compromise spray uniformity, deposition, and
weed control\textsuperscript{22} (Moraes et al.~2021).

The use of spray shields or hoods is another strategy to mitigate spray
drift during pesticide applications.\textsuperscript{22--26} These
devices generally reduce spray drift potential by minimizing spray
exposure to wind. Foster et al.~(2018)\textsuperscript{24} reported that
a hooded sprayer reduced spray drift potential in approximately 50\%
regardless of the nozzles used compared to conventional applications.
The use of spray hoods can potentially extend the available time for
applications during windy conditions and allow the use of finer droplets
with lower carrier volumes to optimize spray coverage and weed
control.\textsuperscript{22} Although the benefits of sprayer hoods have
been studies and reported since the early fifties, the technique
adoption has been relatively low among farmers and
applicators.\textsuperscript{13} With the increased usage of dicamba and
2,4-D and the spray drift incidents associated with both herbicides,
crop protection professionals renewed their interest in spray hoods to
further mitigate herbicide off-target movement during applications.
Therefore, the objective of this study was to evaluate the effectiveness
of spray hoods in reducing pesticide drift for spray solutions and
nozzles typically used for new auxinic herbicide products.

@@

The statistical analyses were conducted with R statistical software
version 4.1.0.\textsuperscript{27} Data analyses were performed with
Bayesian inference with ``brms'' package.\textsuperscript{28} Bayesian
inference uses Markov chain Monte Carlo algorithms for sampling a
probability distribution;\textsuperscript{28} and avoids singular fit
from frequentist linear models when using complex random effects.

@@

Data was fitted to a mixed model using \emph{brm} function. Treatments
were the fixed effects and blocks nested within location random effects.
Model family was gaussian and prior distribution was set to student-t
with mean 0.5, standard deviation 3 and 11 degrees of freedom. The
posterior summaries (mean and highest posterior density) were estimated
with \emph{emmeans} function from the ``emmeans'' package. Treatment
means were compared using Bayes Factor (BF).\textsuperscript{29,30} In
short, if BF \textgreater{} 1 there is evidence for H1 (difference
between treatments); whereas, if H0 \textless{} 1 there is evidence for
H0 (no difference between treatments). If BF = 1, there is no evidence.
The level of evidence (anecdotal, moderate, strong, very strong, and
extreme) varies as the BF value increases (evidence for H1) or decreases
(evidence for H0).

@@

The area under the curve (AUC) was used to validate the linear models.
The spray solution deposition across distances within an experimental
unit were used to calculate the absolute AUC value. The AUC was
performed with \emph{audps} function from the ``agricolae'' package. The
AUC is commonly used for plant disease progress\textsuperscript{31,32}
but has been used to calculate herbicide injury.\textsuperscript{33}
Data was fitted to a mixed model using \emph{brm} function. Treatments
were the fixed effects and blocks nested within location random effects.
Model family was gaussian and prior distribution was set to student-t
with mean 0.5, standard deviation 3 and 11 degrees of freedom. The
posterior summaries and treatment means were estimated and compared
using Bayes Factor (BF) as above-mentioned.

@@

The Dv(10,50,90), RS, and \% drifable fines was fitted to a Bayesian
linear mixed model using \emph{brm} function. In the models, solution
and nozzle were set as fixed effects. Model family was hurdle gamma and
prior distribution was set to student-t with mean 0.5, standard
deviation 1 and 2 degrees of freedom. For each response variable, two
models were fitted: with and without interaction (solution and nozzle).
A model comparison was made with \textbf{bayesfactor\_models} from
``bayestestR'' package\textsuperscript{34} to investigate interaction
significance. For all response variables (Dvs, RS and \% drifable
fines), the best model was with interaction. The posterior summaries and
treatment means were estimated and compared using Bayes Factor (BF) as
above-mentioned.

@@

\hypertarget{droplet-size}{%
\subsection{Droplet size}\label{droplet-size}}

As expected, the TTI nozzle produced coarser spray classification
compared to the ULD and the AIXR nozzles across all spray solutions
tested. In a response surface modeling approach in which nozzles were
tested at different operational setups, TTI nozzles had greater
percentage of operational setups producing Ultra Coarse (90\%) spray
classification compared to ULD (2\%) and AIXR (0\%)
nozzles.\textsuperscript{35} Legleiter et al.~(2018)\textsuperscript{36}
reported that glyphosate + 2,4-D (premixture formulation) applications
using a TTI11004 nozzle produced coarser spray classification (Ultra
Coarse) when compared to AIXR11004 (Very Coarse), TT11004 (Coarse), and
XR11004 (Medium) nozzles. Alves et al.~(2020)\textsuperscript{37}
reported that applications of different dicamba formulations using a
TTI110015 nozzle had larger droplet size across all formulations when
compared to applications using an AIXR110015 nozzle. Zaric
(2020)\textsuperscript{38} reported that the TTI11004 nozzle
consistently produced coarser spray droplet size across multiple spray
solutions when compared to the ULD12004 nozzle.

Creech et al.~(2015)\textsuperscript{18} reported that nozzle design had
major effects on spray droplet size, whereas spray solution influenced
droplet spectrum to a less extent. The addition of DRA increased spray
droplet size across all nozzles tested herein. Samples et
al.~(2021)\textsuperscript{39} reported that the addition of DRAs
(polymer and guargum) increased the spray droplet size of herbicide
spray mixtures containing combinations of glyphosate, glufosinate,
acetochlor, \emph{S}-metolachlor, dicamba, fomesafen, and/or 2,4-D
applied with an AIXR11005 nozzle. Zaric (2020)\textsuperscript{38}
reported that the addition of DRAs consistently increased spray droplet
size for dicamba applications using TTI1104 and ULD12004 spray nozzles.
These findings highlight the specific instructions regarding nozzle
selection for the new dicamba products (``Engenia Product Label'' 2021,
``Xtendimax Product Label'' 2021), in which nozzles producing Ultra
Coarse spray classifications are approved for applications. Label
instructions for new 2,4-D formulations are more flexible in terms of
nozzle selection, where Coarse, Very Coarse, and Extremely Coarse spray
classifications are allowed (``Enlist Duo Product Label'' 2021, ``Enlist
One Product Label'' 2021). New dicamba and 2,4-D product labels also
include specific DRAs to be used, especially when products are tank
mixed with other pesticides.

\hypertarget{spray-solution-deposition-in-swath}{%
\subsection{Spray solution deposition
in-swath}\label{spray-solution-deposition-in-swath}}

For conventional applications (open) without DRA, the TTI nozzle had
greater in-swath spray deposition volume on petri dishes compared to the
ULD and AIXR nozzles. It has been previously reported that applications
with Ultra Coarse spray had greater in-swath deposition volume on petri
dishes compared to finer spray classifications.\textsuperscript{40}
Finer sprays have a greater percentage of spray volume comprised of
small droplets that are more susceptible to spray
drift.\textsuperscript{19} These small droplets have more aerodynamic
drag and lose their initial momentum rapidly, therefore having their
trajectory highly influenced by the wind compared to coarser
droplets.\textsuperscript{41} It is important to highlight that greater
spray deposition volume collected on petri dishes does not mean greater
spray coverage, as coarser sprays result in reduced spray coverage when
compared to finer spray classifications.\textsuperscript{36,41}

For conventional applications (open), the addition of DRA consistently
increased in-swath spray deposition volume (petri dishes) compared to
applications without DRA. Samples et al.~(2021)\textsuperscript{39}
reported that the addition of DRAs (polymer and guargum) to several
herbicide tank mixtures had inconsistent deposition results on soybean
and cotton when compared to herbicide applications without adjuvants.
Authors reported that while the addition of polymer and guargam based
adjuvants increased cotton spray deposition for glyphosate + dicamba +
\emph{S}-Metolachlor spray mixture, the same adjuvants had no effect or
decreased cotton spray deposition when mixed to glyphosate + 2,4-D.
Moraes et al.~(2021) (Moraes et al.~2021) reported that the addition of
DRAs could have a negative effect on spray uniformity, especially with
nozzles producing coarser spray classifications at lower spray
pressures.

Results reported herein indicate an inconsistent effect of hooded
sprayers on in-swath spray deposition. For applications with DRA, the
conventional sprayer (open) had greater in-swath deposition compared to
hooded applications. On the other hand, for applications without DRA,
the hooded sprayer had greater in-swath deposition compared to the
conventional sprayer. Wolf et al.~(1993)\textsuperscript{22} observed
that solid spray shields generally decreased in-swath deposition
uniformity. Authors noted that spray solution dripping from sprayer
shield walls could increase the in-swath deposition variability during
applications. Wolf et al (1993)\textsuperscript{22} and Moraes et
al.~(2021) observations could explain the lower spray deposition
obtained for hooded applications with the addition of the DRA, although
this hypothesis needs to be further investigated.

@@

For conventional (open) applications without DRA, the TTI nozzle had
less drift potential compared to AIXR and ULD nozzles, as expected.
Alves et al.~(2020)\textsuperscript{37} reported similar results in a
wind tunnel study, where applications of different dicamba formulations
using a TTI nozzle had less spray drift compared to applications using
an AIXR nozzle. Authors reported that soybean plants were still showing
50\% biomass reduction from 9.9 to 13.4 m downwind the nozzle for
applications with the AIXR nozzle, whereas this distance range was
reduced to 6.4 to 7.2 m for applications using the TTI nozzle. In
another wind tunnel study, Alves et al.~(2017)\textsuperscript{42}
reported that dicamba applications with a TTI nozzle had 0.6\% spray
drift at 12 m downwind the nozzle, whereas applications with XR, TT, and
AIXR nozzles had 13.5, 6.6, and 3.2\% drift, respectively. As previously
reported,\textsuperscript{17,43} the addition of DRA reduced spray drift
across all nozzles tested herein.

Hooded applications substantially reduced spray drift potential across
all treatment scenarios. For instance, hooded applications using the
AIXR nozzle without DRA had similar drift potential compared to
conventional applications using the TTI nozzle with DRA despite the
major droplet size differences between these treatments. These results
indicate that the adoption of spray hoods combined with proper nozzle
selection and the addition of DRAs to the spray solution can
substantially reduce spray drift potential during pesticide
applications. Foster et al.~(2018)\textsuperscript{24} reported that the
advent of spray hood considerably reduced spray drift for glyphosate
applications using Fine, Medium, Very Coarse, and Ultra Coarse spray
qualities. In a wind tunnel study, Ozkan et
al.~(1997)\textsuperscript{25} reported that several spray shields were
effective in reducing spray drift, where a double-foil shield reduced
spray drift in 59\% compared to applications without shields. In
laboratory tests, Smith et al.~(1982) reported that a spray shield could
reduce spray drift up to 70\%, although field studies indicated an
inconsistent performance where spray shields either increased or
decreased spray drift during tests.

The results reported in this study highlight the importance of adopting
best management practices during pesticide applications to mitigate
spray off-target movement to the surrounding environment. Hooded
applications with AIXR and ULD nozzles resulted in satisfactory spray
drift reduction despite the finer droplet spectrum compared to the TTI
nozzle. This could have implications for weed control as applications
with Ultra Coarse droplet spectrum have reduced spray coverage compared
to finer spray classifications. Legleiter et
al.~(2018)\textsuperscript{36} reported that glyphosate + 2,4-D
applications with Ultra Coarse (TTI11004) spray had reduced spray
coverage on artificial targets (cards) compared to Medium (XR11004),
Coarse (TT11004), and Very Coarse (AIXR11004) sprays. However, authors
reported that spray droplet spectrum did not influence 2,4-D absorption
in Palmer amaranth (\emph{Amaranthus palmeri}), waterhemp
(\emph{Amaranthus tuberculatus}), giant ragweed (\emph{Ambrosia
trifida}), and horseweed (\emph{Erigeron canadensis}). Increasing the
application carrier volume is one strategy to overcome the reduced
coverage from applications using coarser sprays. Butts et
al.~(2018)\textsuperscript{44} reported that dicamba applications with
Ultra Coarse spray resulted in optimal weed control for applications at
187 L ha-1, whereas Extremely Coarse spray resulted optimal weed control
for glufosinate applications. However, applications with increased spray
carrier volume are less efficient due to additional time and water
requirements during the operation.\textsuperscript{22} Hooded
applications using AIXR and ULD nozzles can provide increased spray
coverage compared to TTI nozzles while having low drift potential, which
allows for applications at reduced carrier volumes.

Because of the substantial drift reduction, applications with hooded
sprayers could also reduce product buffer zone requirements. New dicamba
formulations provide incentives to the use of qualified hooded sprayers
by decreasing the required downwind buffer from 73 m to 33 m (``Engenia
Product Label'' 2021, ``Xtendimax Product Label'' 2021). Although the
benefits associated with hooded sprayers, the technology has not been
well accepted by farmers. Nordby and Skuterud (1974)\textsuperscript{13}
mentioned that farmers could see spray hoods as cumbersome and expensive
devices that do not allow applicators to check nozzles during
applications. Considering the widespread adoption of dicamba and 2,4-D
tolerant crops and the increase in these herbicide usage, hooded
sprayers could be a very effective technique to mitigate spray drift
during pesticide applications.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-behrens2007}{}%
\CSLLeftMargin{1 }
\CSLRightInline{Behrens MR, Mutlu N, Chakraborty S, Dumitru R, Jiang WZ,
LaVallee BJ, \emph{et al.}, Dicamba {Resistance}: {Enlarging} and
{Preserving Biotechnology}-{Based Weed Management Strategies},
\emph{Science} \textbf{316}:1185--1188, {American Association for the
Advancement of Science} (2007).}

\leavevmode\hypertarget{ref-heap2018}{}%
\CSLLeftMargin{2 }
\CSLRightInline{Heap I and Duke SO, Overview of glyphosate-resistant
weeds worldwide, \emph{Pest Management Science} \textbf{74}:1040--1049
(2018).}

\leavevmode\hypertarget{ref-sammons2014}{}%
\CSLLeftMargin{3 }
\CSLRightInline{Sammons RD and Gaines TA, Glyphosate resistance: State
of knowledge, \emph{Pest Management Science} \textbf{70}:1367--1377
(2014).}

\leavevmode\hypertarget{ref-werle2018}{}%
\CSLLeftMargin{4 }
\CSLRightInline{Werle R, Oliveira MC, Jhala AJ, Proctor CA, Rees J, and
Klein R, Survey of {Nebraska Farmers}' {Adoption} of
{Dicamba}-{Resistant Soybean Technology} and {Dicamba Off}-{Target
Movement}, \emph{Weed Technol} \textbf{32}:754--761 (2018).}

\leavevmode\hypertarget{ref-wright2010}{}%
\CSLLeftMargin{5 }
\CSLRightInline{Wright TR, Shan G, Walsh TA, Lira JM, Cui C, Song P,
\emph{et al.}, Robust crop resistance to broadleaf and grass herbicides
provided by aryloxyalkanoate dioxygenase transgenes, \emph{Proceedings
of the National Academy of Sciences} \textbf{107}:20240--20245 (2010).}

\leavevmode\hypertarget{ref-soltaniOfftargetMovementAssessment2020}{}%
\CSLLeftMargin{6 }
\CSLRightInline{Soltani N, Oliveira MC, Alves GS, Werle R, Norsworthy
JK, Sprague CL, \emph{et al.}, Off-target movement assessment of dicamba
in {North America}, \emph{Weed Technol} \textbf{34}:318--330 (2020).}

\leavevmode\hypertarget{ref-werle2021}{}%
\CSLLeftMargin{7 }
\CSLRightInline{Werle R, Mobli A, Striegel S, Arneson N, DeWerff R,
Brown A, \emph{et al.}, Large {Scale Evaluation} of 2,4-{D Choline
Off}-target {Movement} and {Injury} in 2,4-{D}-susceptible {Soybean},
\emph{Weed Technology}:1--22, {Cambridge University Press} (2021).}

\leavevmode\hypertarget{ref-matthews2008}{}%
\CSLLeftMargin{8 }
\CSLRightInline{Matthews G, Pesticide {Application Methods}, {John Wiley
\& Sons} (2008).}

\leavevmode\hypertarget{ref-alheidary2014}{}%
\CSLLeftMargin{9 }
\CSLRightInline{Al Heidary M, Douzals JP, Sinfort C, and Vallet A,
Influence of spray characteristics on potential spray drift of field
crop sprayers: {A} literature review, \emph{Crop Protection}
\textbf{63}:120--130 (2014).}

\leavevmode\hypertarget{ref-arvidsson2011}{}%
\CSLLeftMargin{10 }
\CSLRightInline{Arvidsson T, Bergström L, and Kreuger J, Spray drift as
influenced by meteorological and technical factors, \emph{Pest
Management Science} \textbf{67}:586--598 (2011).}

\leavevmode\hypertarget{ref-felsot2010}{}%
\CSLLeftMargin{11 }
\CSLRightInline{Felsot AS, Unsworth JB, Linders JBHJ, Roberts G, Rautman
D, Harris C, \emph{et al.}, Agrochemical spray drift; assessment and
mitigation---{A} review*, \emph{Journal of Environmental Science and
Health, Part B} \textbf{46}:1--23, {Taylor \& Francis} (2010).}

\leavevmode\hypertarget{ref-hewitt2000}{}%
\CSLLeftMargin{12 }
\CSLRightInline{Hewitt AJ, Spray drift: Impact of requirements to
protect the environment, \emph{Crop Protection} \textbf{19}:623--627
(2000).}

\leavevmode\hypertarget{ref-nordby1974}{}%
\CSLLeftMargin{13 }
\CSLRightInline{Nordby A and Skuterud R, The effects of boom height,
working pressure and wind speed on spray drift, \emph{Weed Research}
\textbf{14}:385--395 (1974).}

\leavevmode\hypertarget{ref-egan2014}{}%
\CSLLeftMargin{14 }
\CSLRightInline{Egan JF, Barlow KM, and Mortensen DA, A
{Meta}-{Analysis} on the {Effects} of 2,4-{D} and {Dicamba Drift} on
{Soybean} and {Cotton}, \emph{Weed Science} \textbf{62}:193--206,
{Cambridge University Press} (2014).}

\leavevmode\hypertarget{ref-etheridge1999}{}%
\CSLLeftMargin{15 }
\CSLRightInline{Etheridge RE, Womac AR, and Mueller TC, Characterization
of the {Spray Droplet Spectra} and {Patterns} of {Four Venturi}-{Type
Drift Reduction Nozzles}, \emph{Weed Technology} \textbf{13}:765--770,
{Cambridge University Press} (1999).}

\leavevmode\hypertarget{ref-hewitt2008}{}%
\CSLLeftMargin{16 }
\CSLRightInline{Hewitt AJ, Spray optimization through application and
liquid physical property variables--{I}, \emph{Environmentalist}
\textbf{28}:25--30 (2008).}

\leavevmode\hypertarget{ref-hilz2013}{}%
\CSLLeftMargin{17 }
\CSLRightInline{Hilz E and Vermeer AWP, Spray drift review: {The} extent
to which a formulation can contribute to spray drift reduction,
\emph{Crop Protection} \textbf{44}:75--83 (2013).}

\leavevmode\hypertarget{ref-creech2015}{}%
\CSLLeftMargin{18 }
\CSLRightInline{Creech CF, Henry RS, Fritz BK, and Kruger GR, Influence
of {Herbicide Active Ingredient}, {Nozzle Type}, {Orifice Size}, {Spray
Pressure}, and {Carrier Volume Rate} on {Spray Droplet Size
Characteristics}, \emph{Weed Technology} \textbf{29}:298--310,
{Cambridge University Press} (2015).}

\leavevmode\hypertarget{ref-dorr2013}{}%
\CSLLeftMargin{19 }
\CSLRightInline{Dorr GJ, Hewitt AJ, Adkins SW, Hanan J, Zhang H, and
Noller B, A comparison of initial spray characteristics produced by
agricultural nozzles, \emph{Crop Protection} \textbf{53}:109--117
(2013).}

\leavevmode\hypertarget{ref-butts2019}{}%
\CSLLeftMargin{20 }
\CSLRightInline{Butts TR, Butts LE, Luck JD, Fritz BK, Hoffmann WC, and
Kruger GR, Droplet size and nozzle tip pressure from a pulse-width
modulation sprayer, \emph{Biosystems Engineering} \textbf{178}:52--69
(2019).}

\leavevmode\hypertarget{ref-butts2021}{}%
\CSLLeftMargin{21 }
\CSLRightInline{Butts TR, Barber LT, Norsworthy JK, and Davis J, Survey
of ground and aerial herbicide application practices in {Arkansas}
agronomic crops, \emph{Weed Technology} \textbf{35}:1--11, {Cambridge
University Press} (2021).}

\leavevmode\hypertarget{ref-wolf1993}{}%
\CSLLeftMargin{22 }
\CSLRightInline{Wolf TM, Grover R, Wallace K, Shewchuk SR, and Maybank
J, Effect of protective shields on drift and deposition characteristics
of field sprayers, \emph{Can J Plant Sci} \textbf{73}:1261--1273, {NRC
Research Press} (1993).}

\leavevmode\hypertarget{ref-burnside1968}{}%
\CSLLeftMargin{23 }
\CSLRightInline{Burnside OC, A {Shielded}, {Tractor}-{Mounted Sprayer}
for {Research Plots}, \emph{Weed Science} \textbf{16}:386--388,
{Cambridge University Press} (1968).}

\leavevmode\hypertarget{ref-foster2018}{}%
\CSLLeftMargin{24 }
\CSLRightInline{Foster HC, Sperry BP, Reynolds DB, Kruger GR, and
Claussen S, Reducing {Herbicide Particle Drift}: {Effect} of {Hooded
Sprayer} and {Spray Quality}, \emph{Weed Technology}
\textbf{32}:714--721, {Cambridge University Press} (2018).}

\leavevmode\hypertarget{ref-ozkan1997}{}%
\CSLLeftMargin{25 }
\CSLRightInline{Ozkan H, Miralles A, Sinfort C, Zhu H, and Fox R,
Shields to {Reduce Spray Drift}, \emph{Journal of Agricultural
Engineering Research} \textbf{67}:311--322 (1997).}

\leavevmode\hypertarget{ref-d.b.smith1982}{}%
\CSLLeftMargin{26 }
\CSLRightInline{D. B. Smith, F. D. Harris, and B. J. Butler, Shielded
{Sprayer Boom} to {Reduce Drift}, \emph{Transactions of the ASAE}
\textbf{25}:1136--1140 (1982).}

\leavevmode\hypertarget{ref-LanguageEnvironmentStatistical2021}{}%
\CSLLeftMargin{27 }
\CSLRightInline{R: {A Language} and {Environment} for {Statistical
Computing}, {R Foundation for Statistical Computing}, {Vienna, Austria}
(2021).}

\leavevmode\hypertarget{ref-burknerBrmsPackageBayesian2017}{}%
\CSLLeftMargin{28 }
\CSLRightInline{Bürkner P-C, \textbf{Brms} : {An} {\emph{R}} {Package}
for {Bayesian Multilevel Models Using} {\emph{Stan}}, \emph{J Stat Soft}
\textbf{80} (2017).}

\leavevmode\hypertarget{ref-leeBayesianCognitiveModeling2014}{}%
\CSLLeftMargin{29 }
\CSLRightInline{Lee MD and Wagenmakers E-J, Bayesian {Cognitive
Modeling}: {A Practical Course}, {Cambridge University Press} (2014).}

\leavevmode\hypertarget{ref-kassBayesFactors1995}{}%
\CSLLeftMargin{30 }
\CSLRightInline{Kass RE and Raftery AE, Bayes {Factors}, \emph{Journal
of the American Statistical Association} \textbf{90}:773--795,
{{[}American Statistical Association, Taylor \& Francis, Ltd.{]}}
(1995).}

\leavevmode\hypertarget{ref-meenaAreaDiseaseProgress2011}{}%
\CSLLeftMargin{31 }
\CSLRightInline{Meena PD, Chattopadhyay C, Meena SS, and Kumar A, Area
under disease progress curve and apparent infection rate of {Alternaria}
blight disease of {Indian} mustard ({Brassica} juncea) at different
plant age, \emph{Archives of Phytopathology and Plant Protection}
\textbf{44}:684--693, {Taylor \& Francis} (2011).}

\leavevmode\hypertarget{ref-simkoAreaDiseaseProgress2011}{}%
\CSLLeftMargin{32 }
\CSLRightInline{Simko I and Piepho H-P, The {Area Under} the {Disease
Progress Stairs}: {Calculation}, {Advantage}, and {Application},
\emph{Phytopathology®} \textbf{102}:381--389, {Scientific Societies}
(2011).}

\leavevmode\hypertarget{ref-striegelSpraySolutionPH2021}{}%
\CSLLeftMargin{33 }
\CSLRightInline{Striegel S, Oliveira MC, Arneson N, Conley SP,
Stoltenberg DE, and Werle R, Spray solution {pH} and soybean injury as
influenced by synthetic auxin formulation and spray additives,
\emph{Weed Technol} \textbf{35}:113--127 (2021).}

\leavevmode\hypertarget{ref-makowski2019}{}%
\CSLLeftMargin{34 }
\CSLRightInline{Makowski D, Ben-Shachar M, and Lüdecke D, {bayestestR}:
{Describing Effects} and their {Uncertainty}, {Existence} and
{Significance} within the {Bayesian Framework}, \emph{JOSS}
\textbf{4}:1541 (2019).}

\leavevmode\hypertarget{ref-fritz2016}{}%
\CSLLeftMargin{35 }
\CSLRightInline{Fritz B, Hoffman W, and Anderson J, Response {Surface
Method} for {Evaluation} of the {Performance} of {Agricultural
Application Spray Nozzles}, \emph{Pesticide Formulation and Delivery
Systems: 35th Volume, Pesticide Formulations, Adjuvants, and Spray
Characterization in 2014}, {ASTM International} (2016).}

\leavevmode\hypertarget{ref-legleiter2018}{}%
\CSLLeftMargin{36 }
\CSLRightInline{Legleiter TR, Young BG, and Johnson WG, Glyphosate plus
2,4-{D Deposition}, {Absorption}, and {Efficacy} on
{Glyphosate}-{Resistant Weed Species} as {Influenced} by {Broadcast
Spray Nozzle}, \emph{Weed Technology} \textbf{32}:141--149, {Cambridge
University Press} (2018).}

\leavevmode\hypertarget{ref-alves2020}{}%
\CSLLeftMargin{37 }
\CSLRightInline{Alves GS, Vieira BC, Ynfante RS, Santana TM, Moraes JG,
Golus JA, \emph{et al.}, Tank contamination and simulated drift effects
of dicamba-containing formulations on soybean cultivars,
\emph{Agrosystems, Geosciences \& Environment} \textbf{3}:e20065
(2020).}

\leavevmode\hypertarget{ref-zaric2020}{}%
\CSLLeftMargin{38 }
\CSLRightInline{Zaric M, Effects of {Tank Contamination} and {Impact} of
{Drift}-{Reducing Agents} on {Weed Control} in {Response} to {Dicamba
Applications}, \emph{Theses, Dissertations, and Student Research in
Agronomy and Horticulture} (2020).}

\leavevmode\hypertarget{ref-samples2021}{}%
\CSLLeftMargin{39 }
\CSLRightInline{Samples CA, Butts TR, Vieira BC, Irby JT, Reynolds DB,
Catchot A, \emph{et al.}, Effect of {Deposition Aids Tank}-{Mixed} with
{Herbicides} on {Cotton} and {Soybean Canopy Deposition} and {Spray
Droplet Parameters}, \emph{Agronomy} \textbf{11}:278, {Multidisciplinary
Digital Publishing Institute} (2021).}

\leavevmode\hypertarget{ref-vieira2018}{}%
\CSLLeftMargin{40 }
\CSLRightInline{Vieira BC, Butts TR, Rodrigues AO, Golus JA, Schroeder
K, and Kruger GR, Spray particle drift mitigation using field corn
({Zea} mays {L}.) As a drift barrier, \emph{Pest Management Science}
\textbf{74}:2038--2046 (2018).}

\leavevmode\hypertarget{ref-knoche1994}{}%
\CSLLeftMargin{41 }
\CSLRightInline{Knoche M, Effect of droplet size and carrier volume on
performance of foliage-applied herbicides, \emph{Crop Protection}
\textbf{13}:163--178 (1994).}
